Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-06 paper/preprint/appendix.Rmd
graphs for cruising milestone (not currently included)

```{r, echo=F, message=F}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
library(stargazer)

@@

```{r, include=F}
# need to also include main effect terms ("age" and "cruise")?
face_cruise_eff <- effects::effect(term="age:cruise", mod=face_cruise)
fc_dat <- data.frame(face_cruise_eff) %>% filter(cruise==0 | cruise==1)
fc_dat %>% ggplot(aes(x=age, y=fit, group=cruise, color=cruise)) +
  geom_line() +
  geom_ribbon(aes(x=age, ymin=lower, ymax=upper, fill=cruise), alpha= 0.3) +
  geom_point(data=face_hand_by_age_milestones, aes(x=age, y=prop_faces))
```

>>>>

```{r, echo=F, message=F}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(egg)
library(stargazer)
library(ggeffects)

@@

```{r, include=F}
f1 <- ggpredict(face_cruise, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on faces seen") + 
  xlab("Age (months)") + ylab("Proportion of faces") + theme_classic()

h1 <- ggpredict(hand_cruise, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on hands seen") + 
  xlab("Age (months)") + ylab("Proportion of hands") + theme_classic()

ggpubr::ggarrange(f1, h1, nrow=1, common.legend=T)
```
